Adopting agile in the large: motivations, success factors and challenges

### 2013-12-03 journal/article.tex
Inter-rater statistics
Inter-rater stats

>>>>

Inter-rater statistics

                    Maria
           excl   ???   incl    TOT
     excl  1578    18    15    1611
Kimi ???     84    17     8     109
     incl    51    42    62     155
     TOT   1713    77    85    1875

???'s =  169
in/ex = 1706

Pr(Kimi, in) = in / (tot)  =  155 / 1857 = 0.0619
Pr(Kimi, ex) = ex / (tot)  = 1611 / 1857 = 0.8675
Pr(Maria, in) = in / (tot) =   85 / 1857 = 0.0458
Pr(Maria, ex) = ex / (tot) = 1713 / 1857 = 0.9225

Pr(e) = Pr(Kimi, in) * Pr(Maria, in) + Pr(Kimi, ex) * Pr(Maria, ex) = 0.8031

Pr(a) = (ex-ex + in-in) / tot = 0.8831

k = 0.4063
